### 2023-09-04 accepted/COPSolver/manuscript.tex
updating COPSolver paper

The first version of the software, COPSolver\_1.0-1, applies the analytical solution method developed by Fraga et al. (2023) to solve the Multi-product Batch Processing Time Maximization (MBPTM) problem. This problem arises in production process operations where a set of products are processed simultaneously on the same machine, but with production rates that can be different for each product. There is a production limit for each product and also for the products group, as well as a limit for the batch processing time. The problem consists of defining the maximum processing time of the multi-product batch respecting the known production limits. The exact analytical method of Fraga et al. (2023) is extremely efficient, proposing solutions very quickly and with low computational cost.

@@

COPSolver is open source software written in C++ language. Its architecture has been planned as follows: solver will be formed by a main.cpp file along with a library set (.h) and their respective source codes (.cpp). Each library will be developed to define and solve a single distinct type of problem. All libraries will contain two main structures called problem and solution, which will be used to define the parameters of the problem and the desired solution, respectively. Each library will also contain a class, called cop (for combinatorial optimization problems) or otherwise according to the nature of the problem addressed. Such class will basically contain functions for constructing/reading the problem, functions for solving the problem, and printing functions. Functions with similar purposes will be named with the same name using the functionalities of polymorphism. The libraries will be distinguished by a distinct namespace containing an acronym for the specific problem in the library itself. The definition of the problems can be done in three distinct ways: (1) through the data.txt file; (2) using solver predefined problems; and (3) generating a problem statically or randomly through pre-established functions of the solver. The config.txt file should be adjusted in order to inform the type of problem desired, as well as to select the method of defining the problem and the parameters that should be adjusted according to the chosen method. In the future, an extra library will be developed for automatic identification of the problem according to the definitions presented and for solution by the best method. For better suitability to the codeocean repository, the computational codes will be allocated within a folder named code, the files containing the input data (config.txt and data.txt) will be allocated within a folder named data, and the output files will be inserted into a folder named results. Also, files containing .h computational codes will be inserted inside a folder named lib while .cpp files (except main.cpp) will be inserted inside a folder named src. The lingo-language solvers developed for COPSolver validation will be available in specific folders within the folder named LINGOSolver.

@@

\node[below=3.7cm of code,doc,fill=green!10] (main) {main.cpp};
\node[left=1cm of main,doc,fill=green!10] (mbptmh) {mbptm.h};
\node[right=1cm of main,doc,fill=green!10] (mbptmcpp) {mbptm.cpp};

@@

\draw[-latex] (mbptmh) -- (main);
\draw[-latex] (fit4.south west) edge [bend left=25]  (fit3.south east);
\draw[-latex] (main) -- (code);

@@

@@

%\draw[-latex] (datalng.east) |- (lingocode.west);

@@

%\draw[-latex] (lingocode) -- (cap);

@@

@@

\draw[-latex] (outputlng) |- (output.east) node[midway,right,font=\small\sffamily,fill=white]{results validation};
\end{tikzpicture}
\end{center}
\caption{Software architecture.}
\end{figure}

@@

COPSolver\_1.0-1 can also be used for teaching and research. It can be used to conduct case studies, assisting in teaching and research. Since COPSolver is built on the basis of libraries, it can also be reused in the development of other more complex software in research and technological projects.

@@

\vskip0.3cm
\noindent
\textbf{Acknowledgements}\\
Huge thanks to the teams responsible for developing elementary OS, as well as google translator, gummi, CodeBlocks, LINGO, git, GitHub, gcc, and TeXLive libraries. Without the availability of these tools, COPSolver could never have been developed. I am also very grateful to my co-workers Regilda da Costa e Silva Menêzes and Marcos Luiz Henrique for their constant support to the projects I develop and to my dear advisees Aldênia Karla Barrêto Candido, Lays Cristiane Cavalcante de Alcântara Aguiar, Edwedja de Lima Silva and Ítalo Ruan Barbosa de Aquino, among others, for having participated so enthusiastically in the projects that gave rise to this software, in particular for having made the effort to describe real processes in such detail. I would also like to thank the company in the plastic bag sector and other companies that made the studies possible as well as the identification of the new optimization problem addressed in COPSolver\_1.0-1. \\

>>>>

The first version of the software, COPSolver\_1.0-1, applies the analytical solution method developed by Fraga et al. (2023) to solve the Multi-product Batch Processing Time Maximization (MBPTM) problem. This problem arises in production process operations where a set of products are processed simultaneously on the same machine, but with production rates that can be different for each product. There is a production limit for each product and also for the products group, as well as a limit for the batch processing time. The problem consists of defining the maximum processing time of the multi-product batch respecting the known restrictions. The exact analytical method of Fraga et al. (2023) is extremely efficient, proposing solutions very quickly and with low computational cost.

@@

COPSolver is open source software written in C++ language. Its architecture has been planned as follows: solver will be formed by a main.cpp file along with a library set (.h) and their respective source codes (.cpp). Each library will be developed to define and solve a single distinct type of problem. All libraries will contain two main structures called problem and solution, which will be used to define the parameters of the problem and the desired solution, respectively. Each library will also contain a class, called cop (for combinatorial optimization problems) or otherwise according to the nature of the problem addressed. Such class will basically contain functions for constructing/reading the problem, functions for solving the problem, and printing functions. Functions with similar purposes will be named with the same name using the functionalities of polymorphism. The libraries will be distinguished by a distinct namespace containing an acronym that identifies the problem addressed in the library itself. The definition of the problems instances can be done in three distinct ways: 1) through the data.txt file; 2) using solver predefined problems; and 3) generating a problem statically or randomly through pre-established functions of the solver. The config.txt file should be adjusted in order to: 1) inform the type of problem addressed; 2) select the method of defining the problem and the parameters that should be adjusted according to the chosen method; and 3) select the method for solving the problem. In the future, an extra library will be developed for automatic identification of the problem according to the definitions presented and for solution by the best method. For better suitability to the codeocean repository, the computational codes will be allocated within a folder named code, the files containing the input data (config.txt and data.txt) will be allocated within a folder named data, and the output files will be inserted into a folder named results. Also, files containing .h computational codes will be inserted inside a folder named lib while .cpp files (except main.cpp) will be inserted inside a folder named src. The lingo-language solvers developed for COPSolver validation will be available in specific subfolders within the folder named LINGOSolver.

@@

\node[below left =3.7cm and -0.65cm of code.south,doc,fill=green!10] (main) {main.cpp};
\node[left=1cm of main,doc,fill=green!10] (mbptmh) {mbptm.h};
\node[right=1cm of main,doc,fill=green!10] (mbptmcpp) {mbptm.cpp};

@@

\draw[-latex] (mbptmh) -- (main);

\node[below=0.5cm of mbptmcpp] (aux6) {};

\draw (mbptmcpp) -- (aux6.center);
\draw[-latex] (aux6.center) -| (mbptmh);

@@

\node[above=0.6cm of fit5, doc,regular polygon,regular polygon sides=8,fill=orange!30, scale=0.8, xscale=1.4] (compiler) {g++};

\draw[-latex] (fit5) -- (compiler);
\draw[-latex] (compiler) -- (code);

@@

@@

@@

\node[above=0.5cm of outputlng, doc, shape=diamond, fill=black!10] (val) {validation};

@@

\draw[-latex] (outputlng) -- (val);
\draw[-latex] (output) -- (val);

\end{tikzpicture}
\end{center}
\caption{Software architecture.}
\end{figure}

@@

COPSolver\_1.0-1 can also be used to conduct case studies, assisting in teaching and research. Also, since COPSolver is built on the basis of problem-oriented libraries, it can also be reused in the development of other more complex software in research and technological projects.

@@

\vskip0.3cm
\noindent
\textbf{Acknowledgements}\\
Huge thanks to the teams responsible for developing elementary OS, as well as google translator, duckduckgo, gummi, CodeBlocks, LINGO, git, GitHub, gcc, and TeXLive libraries. Without the availability of these tools, COPSolver could never have been developed. I am also very grateful to my co-workers Regilda da Costa e Silva Menêzes and Marcos Luiz Henrique for their constant support to the projects I develop and to my dear advisees Aldênia Karla Barrêto Candido, Lays Cristiane Cavalcante de Alcântara Aguiar, Edwedja de Lima Silva and Ítalo Ruan Barbosa de Aquino, among others, for having participated so enthusiastically in the projects that gave rise to this software, in particular for having made the effort to describe real processes in such detail. I would also like to thank the company in the plastic bag sector and other companies that made the studies possible as well as the identification of the new optimization problem addressed in COPSolver\_1.0-1. \\
